---
title: "Data Cleansing & Preprocessing"
author: "Di Lu"
date: "September 16, 2018"
output: html_document
---

*This script is to cleanse and preprocess data.*
```{r load libraries and sources, message=FALSE, warning=FALSE, include=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)

source("../lib/preprocess.R")
```

## 1. Read the original happy moment data.
```{r read data, message=FALSE, warning=FALSE}
hm_data <- read_csv("../data/cleaned_hm.csv")
```

## 2. Clean the data.
The starter code provides a very well designed preprocessing procedure. This chunk uses `extract_keywords` function, a wrap-up of all method provided in starter code, to make the cleaner. Here I also included a column for the text before stemming and removing stopwords. So, it is more readable.
```{r clean hm data, message=FALSE, warning=FALSE}
hm_data <- extract_keywords(hm_data)
```

## 3. Save the data.
```{r save data, message=FALSE, warning=FALSE}
write_csv(hm_data, "../output/processed_moments.csv")
```
